Computer Science House Constitution

### 2022-02-14 constitution.tex
Waiving of Qualifications: fix typos

\asubsection{Waiving of Qualifications}
\begin{enumerate}
  \item The following Qualifications may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
    \begin{enumerate}
      \item Candidates must reside on floor during the term of office.
      \item Candidates must have at least one full semester of House membership as an Active Member.
      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
    \end{enumerate}
  \item Each vote to waive a qualification may only apply to a single Qualification and a single Selection.
  \item The chair of the vote shall state what qualification waiver is being voted upon, what Selection the waiver will apply to, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if if the waiver passes.
\end{enumerate}

>>>>

\asubsection{Waiving of Qualifications}
\begin{enumerate}
  \item The following Qualifications may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
    \begin{enumerate}
      \item Candidates must reside on floor during the term of office.
      \item Candidates must have at least one full semester of House membership as an Active Member.
      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
    \end{enumerate}
  \item Each vote to waive a Qualification must only apply to a single Qualification and a single Selection.
  \item The chair of the vote shall state what qualification waiver is being voted upon, what Selection the waiver will apply to, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
\end{enumerate}
